### 2020-10-26 manuscript/manuscript.rmd
reknit

---
bibliography: manuscript.bib
csl: nature.csl
header-includes:
   - \usepackage{lineno}
   - \linenumbers
output:
  word_document: default
  pdf_document:
    latex_engine: xelatex
  html_document: default
  github_document: default
---

>>>>

---
bibliography: manuscript.bib
csl: nature.csl
header-includes:
   - \usepackage{lineno}
   - \linenumbers
output:
  html_document: default
  pdf_document:
    latex_engine: xelatex
  word_document: default
  github_document: default
---
